Hydraulically-vulnerable trees survive on deep-water access in a tropical forest community

### 2020-10-22 manuscript.rmd
1. Updated description of LAI seasonality

---
title: "Hydraulically-vulnerable trees survive on deep-water access in a tropical forest community"
author: ''
date: ''
output:
  bookdown::pdf_document2: default
  bookdown::html_document2:
    number_sections: no
    theme: flatly
    fig_caption: yes
  bookdown::word_document2:
        reference_docx: manuscriptstyle.docx
        fig_caption: yes
bibliography: references.bib
csl: new-phytologist.csl
---

@@

#### Leaf Area Index (LAI)
\
To explore the effect of species seasonality in leaf phenology on growth, we assumed species-specific seasonal curves for leaf area index ($LAI$, range 0-1, unitless). For evergreen species we assumed $LAI$ = 1 throughout the year, whereas for non-evergreen species (various deciduous classes), we assumed $LAI$ = 1 during the wet season (DOY = 150 to 300) given the high forest-level leaf area index for this period (not shown), and obtained an estimate of $LAI$ for the rest of the year as follows. We interpolated species-specific weekly leaf-fall data collected at two similar sites in BCI (1985-2020) to a daily estimate, scaled to express daily leaf fall as a fraction of the total leaf fall in a given year and obtained an average leaf fall fraction by DOY estimate across years ($LeafFall$, range 0-1, unitless). Thus for non-evergreen species, we cumulatively deducted $LeafFall$ from $LAI$ = 1 beginning DOY = 300 and obtained a $LAI$ by DOY curve (Fig. S\@ref(fig:leaf-cover)). We obtained species-specific parameters $A$ & $B$ for Eq. \@ref(eq:k-soil) either from data when available, or a model based on LMA or WSG as described in the earlier section, and used K standardized between 0 and 1 within species (K*) in Eq. \@ref(eq:M-chosen).

@@

>>>>

---
title: "Hydraulically-vulnerable trees survive on deep-water access in a tropical forest community"
author: ''
date: ''
output:
  bookdown::html_document2:
    number_sections: no
    theme: flatly
    fig_caption: yes
  bookdown::pdf_document2: default
  bookdown::word_document2:
        reference_docx: manuscriptstyle.docx
        fig_caption: yes
bibliography: references.bib
csl: new-phytologist.csl
---

@@

#### Leaf Area Index (LAI)
\
To explore the effect of species seasonality in leaf phenology on growth, we assumed species-specific seasonal curves for leaf area index normalised between 0 and 1 (LAI, unitless), using a combination of observations for long-term records of leaf-fall and leaf-lifespan (see SI).

We obtained species-specific parameters $A$ & $B$ for Eq. \@ref(eq:k-soil) either from data when available, or a model based on LMA or WSG as described in the earlier section, and used K standardized between 0 and 1 within species (K*) in Eq. \@ref(eq:M-chosen).

@@

### Leaf Area Index

We generated an estimate of the mean seasonality curve for normalised leaf area index (LAI$*$, range 0-1) for individual species as follows. We interpolated species-specific weekly leaf-fall data collected at two similar sites in BCI (1985-2020) to a daily estimate. We lead this daily leaf-fall time series by the species-specific average leaf-lifespan (in days) and used it as an estimate of the daily leaf-gain time-series. The difference between leaf-fall and leaf-gain gave an estimate of daily leaf-change time series, which was then scaled to express as a fraction of the total leaf fall in a given year. Beginning with the LAI$*$ of 1 at the end of the wet season in the first year of the record, we acccumulated leaf-change over it to obtain a running estimate of the leaf-cover fraction, avaraged it by DOY across years and normalised it to obtain the species-specific seasonality curve in LAI$*$ (range 0-1, unitless). [@Osnas:2018]. (Fig. S\@ref(fig:leaf-cover)).

For five species, an estimate of leaf lifespan was available from direct observations [@Osnan:2018]. For the rest erd.sp.wo.ll species, leaf lifespan was predicted from LMA ($\overline{lifespan} = `r lma.ll.cf[1]` + `r lma.ll.cf[2]`LMA$; *R*^2^ = `r lma.ll.r2`; *p* `r lma.ll.p`, *n* = `r lma.ll.n`).
